---
title: "<h2>Ft. DeSota Buoy Data, Pinellas County</h2>"
output: 
  html_document:
    css: styles.css
runtime: shiny
---

```{r, warning = F, message = F, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F)

library(shiny)
library(plotly)
library(tidyverse)
library(mapview)
library(leaflet)

# dat object
load(url("https://www.github.com/tbep-tech/desoto-buoy/raw/master/data/dat.RData"))

# propscar object
load(url("https://www.github.com/tbep-tech/desoto-buoy/raw/master/data/propscarlines.RData"))

# get data time stamp
log <- readLines('https://www.github.com/tbep-tech/desoto-buoy/raw/master/log.txt')

# columns to pick
pars <- list(
  `Temperature (C)` = 'Temperature',
  `Conductivity (us/cm)` = 'Conductivity', 
  `Salinity (ppt)` = 'Salinity', 
  `pH` = 'pH', 
  `Chlorophyll-a (mg/L)` = 'Chlorophyll-a', 
  `Pheophytin (mg/L)` = 'Pheophytin', 
  `DO (%)` = 'DO%', 
  `DO (mg/L)` = 'DO'
)

# plotly layout
leg <- list(orientation = 'h', xanchor = 'center', x = 0.5)
xxs <- list(title = '')
  
downloadButtonRmd <- function (outputId, label = "Download", class = NULL, ...)  {
  tags$a(id = outputId, class = paste("btn btn-default shiny-download-link", 
                                      class), href = "", target = "_blank", download = NA, 
         icon("download"), label, ...)
}
```

Data current as of `r log`. Source code [here](https://github.com/tbep-tech/desoto-buoy).

```{r reactives}
# data to plot
toplo <- reactive({
  
  # inputs
  parsel <- input$parsel

  out <- dat %>% 
    select(`Station ID`, DateTime, yvar = !!parsel) 
  
  return(out)
  
})

# plotly output
plo <- reactive({
  
  # inputs 
  logsel <- as.logical(input$logsel)
  parsel <- input$parsel
  toplo <- toplo()
  
  ylab <- names(pars)[pars == parsel]
  p <- plot_ly(toplo, x = ~DateTime, y = ~yvar, color = ~factor(`Station ID`), type = 'scatter', mode = 'lines')
  
  if(logsel)
    p <- p %>% 
      layout(
        yaxis = list(title = ylab, type = "log"),
        xaxis = xxs,
        legend = leg
        )
  
  if(!logsel)
    p <- p %>% 
      layout(
        yaxis = list(title = ylab),
        xaxis = xxs,
        legend = leg
        )
  
  return(p)
  
})

scrmap <- reactive({
  
  m <- mapview(propscarlines, layer.name = 'Prop scar length (m)', homebutton = F) %>% 
    .@map
  
  return(m)
  
})
```

```{r}
# wq data
output$wqdwntab <- downloadHandler(
  filename = function(){'wqdat.csv'},
  content = function(file){
    
    # inputs
    toplo <- toplo()
    parsel <- input$parsel
    names(toplo)[names(toplo) %in% 'yvar'] <- parsel
    
    write.csv(toplo, file, quote = T, row.names = F)
    
  }
)
```

# {.tabset}

## Plot and download

```{r}
column(12, 
      column(4, "Select parameter:" ),
      column(4, "Log axis?"),
      column(4, NULL)
)
column(12, 
      column(4, 
             selectInput('parsel', NULL, choices = pars)
             ), 
      column(4, 
             selectInput('logsel', NULL, choices = c(FALSE, TRUE))
             ), 
      column(4, downloadButtonRmd('wqdwntab', 'Download')) 
)
```

<br>
<br>
<br>

```{r}
output$plo <- renderPlotly(plo())
plotlyOutput('plo')
```

## Metadata

### Ft. DeSoto Continuous Monitoring Buoy Data

__Dataset Type__: non-spatial database 

__Name of Data Source__: Ft_DeSoto_Buoys_Data

__Number of Water Resources Sampled__: 2 Sites in Ft Desoto Bay

__Datasource Abbreviation (dataset)__: Ft_DeSoto_Buoy208, Ft_DeSoto_Buoy209

__Description of Datasource__: Continuous water quality data collected by YSI EMM 150 buoys at two locations in Ft DeSoto Bay Pinellas County, Florida.  Data is collected every 15 minutes. Depth of collection is fixed at approximately 0.75 meters from water surface.

__Data Collection Locations__: Buoy 209 is located at 27.629, -82.710.  Buoy 208 located at 27.630 and -82.707. 

__Data Parameters Collected__:  Station ID, Year (yyyy), Time (24 hour, EST), Date (mmddyy), Temperature (ºC), Conductivity (µs/cm), Salinity (ppt), pH, Chlorophyll-a (mg/L), Pheophytin (mg/L), DO % (%), DO (mg/L) 

__Method of Transferring Data to the Atlas__: Transfer via FTP site 

__How Often Data is Transferred to the Atlas__: Quarterly

__Data Current as of__: `r log`

__Disclaimer/Use Constraints__: None 

__Custodian Information__: 

Pinellas County Public Works 

Division of Environmental Management

__Contact Name__: Emma Dontis

__Contact Phone__: (727) 464-4425 

__Contact E-mail__: [edontis@pinellascounty.org](mailto:edontis@pinellascounty.org)

__Contact URL__: [www.pinellascounty.org](www.pinellascounty.org)


